Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-26 02_Paper/paper.tex
talk about svm.

%% The `ecrc' package must be called to make the CRC functionality available
\usepackage{ecrc}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[mode=buildnew]{standalone}% requires -shell-escape
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{dateplot}
\pgfplotsset{compat=newest}

@@

The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
the collection and processing of the data from the process parameters in continous and a few different ML algorithms are used for prediction, 
in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
In addition, it is described in detail how the collected data was collected, prepared and processed.

@@

Our case of study is an abstraction of an assembly process at the industry. The industry 4.0 demonstration cell is composed by three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200. 
The assembly process done at this demostration cell consist on stacking two disk of different size on the top of each other. The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disk. If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
By considering that malfunctions can occur during real production processes at industries, our demonstration cell is able to simulate failures in diverse areas, such as:

@@

We compare Support Vector Machines (SVM), Multilinear Perceptrons
\cite{bishop2006pattern} as well as Random forests in the task of
quality prediction. 
\subsection{Multilinear perceptrons}
These feedforward neural networks typically combine multiple layers
and activation functions. A layer contains a large weight matrix and
a bias vector. To evaluate the layer the input vector must be
multiplied with the weight matrix before the bias vector is added.
Each layer is typically followed by an activation function 
which adds non-linearity to the network graph. Rectified linear units
(ReLUs) are zero for negative inputs leave positive inputs unchanged.
Due to their enormous popularity, we utilize ReLUs here as well.
Since the linear parts of the ReLU and the linear matrix multiplication
are differentiable we can employ gradient descent to train our 
classifier.

\subsection{Support Vector Machines}
Support Vector Machines offer a convex alternative to MLPs \cite{Suykens2002least}.
A convex classifier is guaranteed to converge to a global solution regardless 
of its initialization.

@@

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron (MLP) and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c }
              Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilinear Perceptron & 88 \% \\
              Random Forest          & 98 \%
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilinear Perceptron and 
                Random Forest classification on our annomaly detection task. 
                The first row shows the performance of naively predicting a broken piece
                every time.}
       \label{tab:class_comp}
\end{table}
Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples
quality measurements indicate a problem. This sets the 
baseline over the entire data set, which would be obtained by simply labeling all samples
as faulty. Over the test set, we require to classify more than 64\% of the data correctly.
We would therefore expect any naive classifier to produce at least 64\% accuracy, which we have to beat. In Table~\ref{tab:class_comp}, we observe that this is indeed the case for all three approaches evaluated here. We found the random forest performed best followed by the multilinear
perceptron and the support vector machine.

>>>>

%% The `ecrc' package must be called to make the CRC functionality available
\usepackage{ecrc}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[mode=buildnew]{standalone}% requires -shell-escape
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{booktabs}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{dateplot}
\pgfplotsset{compat=newest}

@@

The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
the collection and processing of the data from the process parameters in continuous and a few different ML algorithms are used for prediction, 
in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
In addition, it is described in detail how the collected data was collected, prepared and processed.

@@

Our case of study is an abstraction of an assembly process at the industry. The industry 4.0 demonstration cell is composed by three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200. 
The assembly process done at this demonstration cell consist on stacking two disks of different size on the top of each other. The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disks. If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
By considering that malfunctions can occur during real production processes at industries, our demonstration cell is able to simulate failures in diverse areas, such as:

@@

We compare Support Vector Machines (SVM), Multilinear Perceptrons
\cite{bishop2006pattern} as well as random forests in the task of
quality prediction. All three will be introduced next.

\subsection{Multilayer perceptrons}
These feedforward neural networks typically combine multiple layers
and activation functions \cite{bishop2006pattern}.
A layer contains a large weight matrix and
a bias vector. To evaluate the layer the input vector must be
multiplied with the weight matrix before the bias vector is added.
Each layer is typically followed by an activation function 
which adds non-linearity to the network graph. Rectified linear units
(ReLUs) are zero for negative inputs leave positive inputs unchanged.
ReLUs are the recommended activation function for modern neural
networks \cite{goodfellow2016deep} we use these here as well.
Since the linear parts of the ReLU and the linear matrix multiplication
are differentiable we can employ gradient descent to train our 
classifier.

\subsection{Support Vector Machines}
Support Vector Machines (SVM) offer a convex alternative to MLPs \cite{Suykens2002least}.
A convex classifier is guaranteed to converge to a global solution regardless 
of its initialization. 
The Kernel trick allows SVM to solve non-linear classification problems \cite{Suykens2002least} by mapping implicitly mapping the inputs into a higher feature space. Radial basis functions (RBF) are commonly chosen as kernels
\cite{Suykens2002least} we choose to follow this practice as well.

@@

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron (MLP) and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Approach         & accuracy \\ \midrule
              Na\"ive-Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilayer Perceptron & 88 \% \\
              Random Forest          & 98 \% \\ \bottomrule
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilinear Perceptron and 
                Random Forest classification on our annomaly detection task. 
                The first row shows the performance of naively predicting a broken piece
                every time.}
       \label{tab:class_comp}
\end{table}
Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples
quality measurements indicate a problem. This sets the 
baseline over the entire data set, which would be obtained by simply labeling all samples
as faulty. Over the test set, we require to classify more than 64\% of the data correctly.
We would therefore expect any naive classifier to produce at least 64\% accuracy, which we have to beat. In Table~\ref{tab:class_comp}, we observe that this is indeed the case for all three approaches evaluated here. We found the random forest performed best followed by the multilinear
perceptron and the support vector machine.
